### 2011-12-19 doc/theses/mikula/used_technologies_and_definitions.tex
Master thesis: In progress.

@@

\subsection{Conditional Expressions}

\subsection{Quantified Expressions}

\subsection{Built-in Functions}

\subsection{User-defined Functions}

\subsection{Value Comparison Expressions}

\subsection{General Comparison Expressions}

\subsection{Node Comparison Expressions}

\subsection{Usage Examples}

@@

>>>>

In the remainder of this section, basic features of the XQuery languages are briefly described. Many query samples can be found in  chapter \ref{CHAPTER_analysis_of_xquery}.

@@

\subsection{Conditional Expressions}
XQuery provides common \texttt{if-than-else} conditional expressions with common syntax.
\begin{alltt}
if (\(condition\))
than \(expr1\)
else \(expr2\)
\end{alltt}
If $condition$ expression evaluates to true, $expr1$ is evaluated, else $expr2$ is evaluated. The else branch is optional.

\subsection{Quantified Expressions}
XQuery provides two types of quantified expressions, \texttt{every} and \texttt{some}. Their syntax follows.
\begin{alltt}
every \(var\) in \(expr1\)
satisfies \(expr2\)
\end{alltt}
\begin{alltt}
some \(var\) in \(expr1\)
satisfies \(expr2\)
\end{alltt}

Firstly, $expr1$ is evaluated, and then the result of the quantified expression is true if $expr2$ is true for every (some) item, represented by $var$, of the result of $expr1$ (which is a sequence).

\subsection{Functions}
XQuery provides a wide set of built-in functions. \todo{ref?}

And also new functions can defined using the following syntax.
\begin{alltt}
define function \(name\)(\(parameters\)) as \(type\)
\{
  \(expr\)
\}
\end{alltt}
where $name$ is the function's name, $parameters$ is a list of parameters (with or without specification of their types), and $type$ is a type of a return value, which is the result of $expr$.

\subsection{Comparison Expressions}
Comparison expressions are of three types: $value$ comparison expressions, $general$ comparison expressions, and $node$ comparison expressions. A very brief insight follows. More details can be found in REF\todo{ref, moze to takto ostat?}.

The $value$ comparison expressions use operators \texttt{lt}, \texttt{gt}, \texttt{le}, \texttt{ge}, \texttt{eq}, and \texttt{ne} and they compare operands that are or can be converted to atomic values.

The $general$ comparison expressions use operators \texttt{<}, \texttt{>}, \texttt{<=}, \texttt{>=}, \texttt{=}, and \texttt{!=} and they can also compare sequences.

And the $node$ comparison expressions use operators \texttt{is}, \texttt{<<}, and \texttt{>>} and they compare nodes, their identities and order.

@@

\section{Other Technologies}

\begin{description}
\item[XSLT] e\textbf{X}tensible \textbf{S}tylesheet \textbf{L}anguage \textbf{T}ransformations \cite{Clark:99:XTV} is a language to transform input XML document(s) into other (not necessarily XML) document(s).
\end{description}
